Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-18 awipev-CO2.Rmd

>>>>

    + 1: good data
    + 3: impossible date and time test
    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
    + 6: failing the manufacturer range test (not used)
    + 7: failing the regional range test 
    + 12: failing the spike test (NAs from despike)
    + 13: failing the gradient test
    + 15: the instrument was not deployed or operated
    + 99: failing the final visual inspection of the data.
